Characterizing subarctic European vegetation for land surface modeling of ozone pollution and climate risk

### 2021-09-27 VegOzone.tex
Remove subsection and add reference to gap-filling paper

\subsection{2018/19 growing season}
\label{subsec:growing_season_1819}

@@

\section{Statistical analysis}
\label{sec:stats}
In this section, we assess the climate conditions. To this end, we compute multi-annual mean (referred to as climatology in the following) of environmental key variables (temperature, precipitation, global irradiance) and ground-level \chem{[O_3]} at Svanhovd. For the growing seasons 2018/19, we evaluate the statistical significance of divergences from the norm in these variables (referred to as anomalies). We perform a bias correction accounting for the increase in tropospheric background \chem{[O_3]} and cross-calibrate the derived climatology for Svanvik with long-term observations of \chem{[O_3]} at Esrange and Pallas.

>>>>

@@

\section{Statistical analysis}
\label{sec:stats}
In this section, we assess the climate conditions. To this end, we compute multi-annual mean (referred to as climatology in the following) of environmental key variables (temperature, precipitation, global irradiance) and ground-level \chem{[O_3]} at Svanhovd. For the growing seasons 2018/19, we evaluate the statistical significance of divergences from the norm in these variables (referred to as anomalies). We performed a bias correction accounting for the increase in tropospheric background \chem{[O_3]} and cross-calibrate the derived climatology for Svanvik with long-term observations of \chem{[O_3]} at other sites in northern Fennoscandia as described in \citet{ACPD:Falk2021}.
